---
output:
  word_document: default
  html_document: default
---
# Cluster Assignment
## Hailey Hendriks

```{r}
library(tidymodels)
library(tidyverse)
```

```{r}
trucks <- read_csv("trucks.csv")
```

### Task 1
```{r}
ggplot(trucks,aes(Distance, Speeding)) + geom_point()
```

There does seem to be natural clustering for speeding. This appears when the distance is between 25 to 75, and again when the distance is between 150 to 225. 

### Task 2
```{r}
kmeans_recipe = recipe(~ Speeding + Distance, trucks)

trucks_dummy = kmeans_recipe %>%
  step_scale(all_numeric()) %>%
  step_center(all_numeric())

trucks_dummy = prep(trucks_dummy, trucks)

trucks_cleaned = bake(trucks_dummy, trucks)
```

### Task 3
```{r}
set.seed(64)
clusts = 
  tibble(k = 2) %>% 
  mutate(
    kclust = map(k, ~kmeans(trucks_cleaned, .x)),
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, trucks_cleaned)
  )

clusts
```

```{r}
clusters =
  clusts %>%
  unnest(cols = c(tidied))

assignments = 
  clusts %>% 
  unnest(cols = c(augmented))

clusterings = 
  clusts %>%
  unnest(cols = c(glanced))
```

```{r}
p1 = ggplot(assignments, aes(x=Distance,y=Speeding)) + 
  geom_point(aes(color=.cluster), alpha=0.8) +
  facet_wrap(~ k)
p1
```

The clusters are distributed between 1 and 2 with no outliers.

### Task 4
```{r}
set.seed(412)
clusts2 = 
  tibble(k = 1:8) %>% 
  mutate(
    kclust = map(k, ~kmeans(trucks_cleaned, .x)),
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, trucks_cleaned)
  )

clusts2
```

```{r}
clusters2 =
  clusts2 %>%
  unnest(cols = c(tidied))

assignments = 
  clusts2 %>% 
  unnest(cols = c(augmented))

clusterings = 
  clusts2 %>%
  unnest(cols = c(glanced))
```

```{r}
p2 = ggplot(assignments, aes(x=Distance,y=Speeding)) + 
  geom_point(aes(color=.cluster), alpha=0.8) +
  facet_wrap(~ k)
p2
```
K values 2 or 4 seem to be most appropriate for this data. Any other k value does not seem appropriate, as the splits do not fit correctly with the data.

### Task 5
```{r}
ggplot(clusterings, aes(k, tot.withinss)) +
  geom_line() +
  geom_point() + theme_bw()
```

The value of k that seems to be the best is 4 because this is where the bend is at.

### Task 6
```{r}
set.seed(64)
clusts = 
  tibble(k = 4) %>% 
  mutate(
    kclust = map(k, ~kmeans(trucks_cleaned, .x)),
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, trucks_cleaned)
  )

clusts
```

```{r}
clusters =
  clusts %>%
  unnest(cols = c(tidied))

assignments = 
  clusts %>% 
  unnest(cols = c(augmented))

clusterings = 
  clusts %>%
  unnest(cols = c(glanced))
```

```{r}
p1 = ggplot(assignments, aes(x=Distance,y=Speeding)) + 
  geom_point(aes(color=.cluster), alpha=0.8) +
  facet_wrap(~ k)
p1
```

This k value seems to be the best for this data. It created 4 clear groups without any outliers or unclear data.

