---
output:
  word_document: default
  html_document: default
---
## R and RStudio Refresher Assignment
### Hailey Hendriks

### Task 1
```{r}
#install.packages(tidyverse)
#install.packages(esquisse)
library(tidyverse)
library(esquisse)
```

### Task 2
```{r}
diamonddata = diamonds
#str(diamonddata)
```

### Task 3
```{r}
ggplot(diamonddata,aes(x=carat,y=price)) +
  geom_point()
```
As carat size increases, price increases.

### Task 4
```{r}
ggplot(diamonddata,aes(x=carat,y=price,color=cut)) +
  geom_point()
```
As carat size increases, price increases. The better the cut, the smaller the carat size and the more expensive.

### Task 5
```{r}
ggplot(diamonddata,aes(x=carat,y=price,color=cut,)) +
  geom_point() +
  facet_wrap(~color)
```
The worse cut diamonds show up more in the worse colors and at lower prices per carat. The nicer color the diamond, the more expensive and it usually has a better cut.

### Task 6
```{r}
inventory <- read_csv("InventoryData.csv")
#str(inventory)
#summary(inventory)
```

### Task 7
```{r}
inventoryA <- inventory %>%
  filter(Supplier=="A")
#str(inventoryA)
```
This new data frame has 3,695 rows.

### Task 8
```{r}
inventoryA =mutate(inventoryA, OnHandRatio =`On Hand`/`Annual Demand`)
#summary(inventoryA)
```
This line of code created a new column called OnHandRadio that divided the On Hand variable by the Annual Demand variable.

### Task 9
```{r}
avg_cost <- inventoryA  %>%
  group_by(`Item SKU`) %>%
  summarize(SKUAvgCost = mean(`Cost per Unit ($)`))
```

### Task 10
There were no specific topics I found challenging, I just found the syntax to be challenging at times and very tedious. 